Automatic predicate testing in formal certification

### 2016-02-15 ProofsAndTests/paper-TAP/paper-TAP.tex
abstract finished

\begin{abstract}
The use of formal methods helps to increase the confidence in critical software. However, a formal proof is only a guarantee relative to a formal specification, and not necessary about the real requirements. These real requirements are expressed in a natural language like english, and there is always a jump when going from an informal specification to a formal specification, expressed in a logical theory. Thus, proving the correctness about a piece of software always makes the implicit assumption that there is adequacy between the formalised specification, written with predicates, and the real requirements. Unfortunately, a huge part of the complexity lies precisely in the specification itself, and it is far from obvious that the formal specification says exactly and completely what it should say. Why should we trust more these predicates than the code that we've first refused to trust blindly, leading to these proofs? We show in this paper that the proving activity hasn't replaced the testing activity. Instead, it has changed the object which requires to be tested. We show recent ideas about how to deal with this new kind of tests, which includes how to automate them as far as possible.
\keywords{Formal certification, specification, predicate testing, proofs, tests, requirements}
\end{abstract}

>>>>

\begin{abstract}
The use of formal methods helps to increase the confidence in critical software. However, a formal proof is only a guarantee relative to a formal specification, and not necessary about the real requirements. These real requirements are expressed in a natural language, like english, and there is always a jump when going from an informal specification to a formal specification expressed in a logical theory. Thus, proving the correctness of a piece of software always makes the implicit assumption that there is adequacy between the formalised specification --written with logical statements and predicates-- and the real requirements. Unfortunately, a huge part of the complexity lies precisely in the specification itself, and it is far from obvious that the formal specification says exactly and completely what it should say. Why should we trust more these predicates than the code that we've first refused to trust blindly, leading to these proofs? We show in this paper that the proving activity hasn't replaced the testing activity but has only changed the object which requires to be tested. Instead of testing code, we now need to test predicates. We will show how to identify what needs to be tested in this new context. We also present recent ideas about how to conduct these tests on a few examples, and how to automate them as far as possible.

\keywords{Formal certification, specification, predicate testing, formal proof, tests, requirements}
\end{abstract}
